---
title: "MODEL_TITLE_PLACEHOLDER – Development & Documentation"
author: "Model SME"
format: html
params:
  model_id: "MODEL_ID_PLACEHOLDER"
---

```{r}
#| echo: false
library(nzera)
model_id <- params$model_id
meta   <- get_model_metadata(model_id)
schema <- get_model_schema(model_id)
````

# 1. Overview

* **Model ID:** `r meta$id`
* **Title:** `r meta$title`
* **Version:** `r meta$version`
* **Status:** `r meta$status`
* **Owners:** `r paste(meta$owners, collapse = ", ")`

## 1.1 Purpose

Describe the purpose of this model in 3–5 sentences.

# 2. Literature and sources

List key references and data sources (you can expand beyond `meta$references`).

# 3. Conceptual model and equations

...

# 4. Data requirements and structure

```{r}
## document the schema
```

# 5. Step-by-step implementation (development log)

(Working code, experiments, validation, etc.)

# 6. Finalised algorithm (for extraction)

...

# 7. Limitations and uncertainties

...

# 8. Decision log and change log

(Use tables for decisions and changes.)

